\begin{minipage}[c]{1.05\textwidth} \centerline{Towards a Continuous Hyperparameter} \centerline{Representation for Neural Networks} \end{minipage}

### 2017-07-10 docs/manuscript/main.tex

\begin{itemize}
	\item \href{https://onedrive.live.com/edit.aspx/Documents/Machine%20Learning?cid=c05fef92a4e2f5cd&id=documents&wd=target%28Continuous%20Parameterization.one%7C577F6089-A9C8-40F1-A37C-474241ED5D20%2F%29
onenote:https://d.docs.live.net/c05fef92a4e2f5cd/Documents/Machine%20Learning/Continuous%20Parameterization.one#section-id={577F6089-A9C8-40F1-A37C-474241ED5D20}&end}{Continuous Hidden Dimension}
	\item \textbf{Some Thoughts on Local Search on Hidden Units.} Let $\scriptn$ be the $\mathfrak{n}$-discrete instatntiation of the following DFM
	\begin{equation*}
	\begin{tikzcd}
		\scripto: \boxed{\mathbb{R}^n} \arrow{r}{\mathfrak{d}} & \boxed{L^1(E(\gamma))} \arrow{r}{\mathfrak{f}} & \boxed{\mathbb{R}}
	\end{tikzcd}
	\end{equation*}
	where $E: \mathbb{R} \to \scriptl(\mathbb{R})$ is a function which parameterizes the domain over which the $\mathfrak{f}$-functional integrates.

@@

	Thus we are led to the question: \emph{Is hyperparameter search a matter of immediate model accuracy or expected capacity for accuracy, and in that distinction, does optimizing hyperparameters with respect to model accuracy coorespond to optimization on model capactiy and visa versa?}  Let us examine this question in the following context. \

@@

	Baring that local search doesn't necisarrily yield the desired properties, we might now consider a global search.
	The more general setting is of course considering $E$ as a function of variable support geometry. In particular let $E: C^{\infty}_*(\mathbb{R}) \to \scriptl(\mathbb{R})$ so that $f \mapsto \text{supp}(|f|/2 + f/2).$ Not that $C^{\infty}_*(\mathbb{R})$ is the set of infinitely differentiable functions which vanish on at most a $\mu$-null set. Then computation of a gradient descent step becomes a variational problem
	\begin{equation*}
		\begin{aligned}
			\frac{\delta F}{\delta f} &= \frac{\partial F}{\partial y^2} \frac{\delta y^2}{\delta f}  \\
			&= \frac{\partial F}{\partial y^2} \left[\frac{\delta}{\delta f} \int_{E(f)} y^1 \omega_1\ d\mu \right]_{\mathfrak{n}} \\
			&= \frac{\partial F}{\partial y^2} \left[\frac{\delta}{\delta f} \lim_{\kappa \to \infty}\int_{\reals} {\sigma}(\kappa f) y^1 \omega_1\ d\mu \right]_{\mathfrak{n}}
		\end{aligned}
	\end{equation*}

>>>>

\begin{itemize}
	\item \href{https://github.com/MadcowD/conthyperrep/blob/master/docs/notes/note1.pdf}{Continuous Hidden Dimension}
	\item \textbf{Some Thoughts on Local Search on Hidden Units.} Let $\scriptn$ be the $\mathfrak{n}$-discrete instatntiation of the following DFM
	\begin{equation*}
	\begin{tikzcd}
		\scripto: \boxed{\mathbb{R}^n} \arrow{r}{\mathfrak{d}} & \boxed{L^1(E(\gamma))} \arrow{r}{\mathfrak{f}} & \boxed{\mathbb{R}}
	\end{tikzcd}
	\end{equation*}
	where $E: \mathbb{R} \to \scriptl(\mathbb{R})$ is a function which parameterizes the domain over which the $\mathfrak{f}$-functional integrates.

@@

	Thus we are led to the question: \emph{Is hyperparameter search a matter of immediate model accuracy or expected capacity for accuracy, and in that distinction, does optimizing hyperparameters with respect to model accuracy coorespond to optimization on model capactiy and vice versa?}  Let us examine this question in the following context. \

@@

	Baring that local search doesn't necessarily yield the desired properties, we might now consider a global search.
	The more general setting is of course considering $E$ as a function of variable support geometry. In particular let $E: C^{\infty}_*(\mathbb{R}) \to \scriptl(\mathbb{R})$ so that $f \mapsto \text{supp}(|f|/2 + f/2).$ Not that $C^{\infty}_*(\mathbb{R})$ is the set of infinitely differentiable functions which vanish on at most a $\mu$-null set. Then computation of a gradient descent step becomes a variational problem
	\begin{equation*}
		\begin{aligned}
			\frac{\delta F}{\delta f} &= \frac{\partial F}{\partial y^2} \frac{\delta y^2}{\delta f}  \\
			&= \frac{\partial F}{\partial y^2} \left[\frac{\delta}{\delta f} \int_{E(f)} y^1 \omega_1\ d\mu \right]_{\mathfrak{n}} \\
			&= \frac{\partial F}{\partial y^2} \left[\frac{\delta}{\delta f} \lim_{\kappa \to \infty}\int_{\reals} {\sigma}(\kappa f) y^1 \omega_1\ d\mu \right]_{\mathfrak{n}}
		\end{aligned}
	\end{equation*}
